
---
title: "CB[2] Sound"
author: "Wyatt Ogden, Yirui Sun, Trevor Fernstrom, Aaron Dodge"
date: "November 30, 2020"
output:
   html_document:
    Theme: cerulean
    code_folding: hide
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pander)
library(mosaic)
library(car)


hearing <- read_csv("hearing.csv")

hearing$degrees <- abs(hearing$degrees)
hearing$person <- as.factor(hearing$person)
hearing$distance <- as.factor(hearing$distance)
hearing$volume <- as.factor(hearing$volume)
```




## Introduction

One of our key way of location is the sense of sound. We usually are able generally to distinguish where a sound is coming from. We will be testing how distance from the sound paired with volume of the sound affects the ability to determine the sound source location. We will have use a phone with a generic sound at distances of 3 ft, 5 ft, and 7 ft away from the observer, along with testing volume percentage of 10%, 30% and 50% of max volume of the phone.

$$
  Y_{ijk} = \mu + \alpha_i + \beta_{j} + \gamma_k + (\alpha\gamma)_{ik} +\epsilon_{ijk}
$$

**Independent Variable or Treatment:** 1st factor: distance sound is from the observer,  2nd factor: Volume of sound

**Dependent variable:** Distance in degrees from sound

**Material:** Block: helpers


there are three different hypothesies

one for the first factor

$$
  H_0: \alpha_1 = \alpha_2 = \ldots = 0
$$
$$
  H_a: \alpha_i \neq 0 \ \text{for at least one distance} 
$$

One for the second factor
$$
  H_0: \gamma_1 = \gamma_2 = \ldots = 0
$$
$$
  H_a: \gamma_j \neq 0 \ \text{for at least one volume}
$$

One for the interaction of the two factors:
$$
  H_0: \text{The effect of distance} \ \text{is the same for all levels of volume}
$$
$$
  H_a: \text{The effect of distance} \text{is different for at least one level of distance}
$$

$$
\alpha = .05
$$

</br>

## Method

</br>

We will begin by having the observer sit in a spinning chair in the middle of a room blindfolded. We will have one person with the phone at the distance volume combinaiton of the current experiment. They will play the sound and ask the observer to point their arm to where they think the sound is coming from. We will have a 2nd person then measure the distance is degrees of the difference of where they are pointing their arm to and the person holding the phone that is producing the sound. We will repeat this over and over until we have collected data for each possible combination. The person holding the phone will move around the observer so it isn't coming from the same direction each time. We will have each combinaiton be in the same spot for each block so it has a mitigated effect between blocks. We will have marking in the room so that the person producing the sound will be able to accurately repeat them. We will have the person be blindfolded before they get into the room so they are unable to see the marking and have some bias. We will run all the tests in the same space so that ambiant noise and acoustics of the room is also mitigated. To help the person who is moving around and producing the sound we will find a room the is fairly open with minimal chairs, desks, and other objects in the room.

</br>

## Analysis

</br>

```{r}



hearing %>% 
  ggplot(aes(x = distance, y = degrees, shape = volume, color = person)) +
  geom_point(size = 2) +
  labs(title = "Degrees off of sound grouped by distance") +
  theme_bw() 


hearing %>% 
  ggplot(aes(x = volume, y = degrees, shape = distance, color = person)) +
  geom_point(size = 2) +
  labs(title = "Degrees off of sound grouped by volume") +
  theme_bw()




```






```{r}
hearing.aov <- aov(degrees ~ volume * distance + person, data = hearing,
                   contrasts = list(volume = contr.sum,
                                    distance = contr.sum,
                                    person = contr.sum))

pander(summary(hearing.aov))

dummy.coef(hearing.aov)
```

## Diagnostic plots

</br>

```{r}
par(mfrow=c(1,2))
plot(hearing.aov, which = 1:1)
qqPlot(hearing.aov$residuals, main = "QQ Plot of Residuals")

par(mfrow=c(1,1))

```

The residuals vs fitted plot looks to be highly violated, the variance is not constant at all. The qqPlot looks to be mostly fine except for point 22 that is an outlier. Since these two diagnostic plots are both violated, we will run a levene test to double check.


```{r}
leveneTest(degrees ~ distance*volume, data = hearing)
```

Running the Levene test also shows that the different test are not significant. We ran the dianostic plots just as a good measure even though the different P values are not significant, so we are not surprised when the levene test comes back saying things are not significant.

</br>

## Conclusion

Based on the information at hand we are able to conclude that we are unable to reject the null hypothesis for any of the different test. All three test volume, distance, and the interaction are not significant. Some ideas we could test to see if things do become significant is have different volume level, so that the range of volume is larger, or increase the distance so that the range of distances is larger. Increasing the range of volume would be a less expensive iteration to test because we could use the same space to test. If we wanted to test a large distance we would need to get a larger space which could then turn into a nuisance factor because we were not testing the spaces acoustics to see if they were significant. At the moment the interaction is also not significant and we may benefit from only testing one of the variables at a time in later iterations however as both variables increase the interaction may also then become significant.


</br>
</br>